\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[bookmarks=false]{hyperref}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{geometry}
\usepackage{url}
\geometry{margin=1in}
\usepackage{xcolor}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\small,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    numbers=none,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=4
}
\lstset{style=mystyle}

\title{\textbf{liteLRU: A MESI-Conscious, Contention-Bounded Approximate LRU via\\
Chunked Bitmask Eviction on Modern Multi-Core Hardware}}
\author{
  xDarkicex \\
  \small Affiliations: libravdb $\cdot$ bitdev $\cdot$ zephyr-systems \\
  \small Contact: \href{mailto:git@libravdb.com}{git@libravdb.com} \\
  \small Repository: \url{https://github.com/xDarkicex/liteLRU}
}
\date{}

\begin{document}

\maketitle

\begin{abstract}
We describe the design and implementation of \texttt{liteLRU}, a fixed-capacity approximate LRU cache targeting multi-core concurrent workloads. The fundamental design question is not \textit{which items to evict}, but \textit{how to perform eviction and recency tracking without serializing the CPU cores that share the cache}. We analyze why conventional data structures---doubly-linked lists, per-node reference counting, and AoS memory layouts---are structurally incompatible with the MESI cache coherency protocol~\cite{mesi} under concurrent access. In particular, we note that under heavy CAS contention on a single cache line, wait time degrades superlinearly due to RFO (Read-For-Ownership) round-trip amplification~\cite{gogc}. We justify a \textbf{hybrid memory architecture}---where heavily mutated lock-free state is allocated off-heap via mmap, while Go pointers remain on the heap---to eliminate garbage collection interference on the hot path without risking dangling pointers~\cite{gogc2018}. We derive a Structure of Arrays (SoA) layout from first-principles cache-line occupancy arguments~\cite{soadesign}. We then derive the Chunked Bitmask CLOCK eviction algorithm~\cite{clock1969} from the observation that tracking recency state across 64 slots fits exactly into a 64-bit integer, enabling $O(1)$ bulk state evaluation using a single hardware \texttt{CTZ} instruction~\cite{inteltzcnt,armclz}. The resulting mechanism yields bounded wait-free reads and contention-bounded writes. We contrast our approach against recent eviction policy research including S3-FIFO~\cite{s3fifo2023} and SIEVE~\cite{sieve2024}, noting that policy-level optimizations are orthogonal to and do not resolve the synchronization bottleneck addressed here. Empirical evaluation on an 8-core ARM architecture yields p99.9 latency of $\sim$1.5~$\mu$s under the fully instrumented scaling workload (see \S 9.3).
\end{abstract}

\section{Background: The Hardware Model}

To reason about concurrent cache design, we first establish a precise model of the hardware execution environment.

\subsection{The CPU Cache Hierarchy}

A modern multi-core processor maintains a private L1 cache (typically 32--64 KiB, 4--5 cycle latency), a private L2 cache (256 KiB -- 1 MiB, $\sim$12 cycle latency), and a shared L3 cache (several MiB, $\sim$40 cycle latency). Main memory sits at approximately 200--300 cycles. The performance implication is stark: a single L1 cache miss costs roughly $40\times$ more than an L1 hit.

The fundamental unit of coherency is the \textbf{cache line}, dependent on the target platform architecture (e.g., $L=64$ bytes on x86\_64, $L=128$ bytes on Apple Silicon). The CPU never fetches individual bytes; it fetches and writes back entire $L$-byte coherence lines.

\subsection{The MESI Coherency Protocol}

The MESI protocol (Modified, Exclusive, Shared, Invalid) was introduced by Papamarcos and Patel~\cite{mesi1984} to maintain coherency across private caches in a multi-processor system. The relevant state transitions are:

\begin{itemize}
    \item A line held in \textbf{Shared} state by multiple cores transitions to \textbf{Invalid} in all other cores when any single core writes to it.
    \item A write to an \textbf{Invalid} line requires a Read For Ownership (RFO)---a broadcast on the CPU interconnect requesting exclusive ownership from all other cores.
\end{itemize}

The critical consequence is \textbf{false sharing}~\cite{falsesharing1993}: if two independent variables, accessed concurrently by two different cores, reside on the same $L$-byte coherence line, a write by one core forces an RFO on the other core's copy, even though the second core is accessing a logically unrelated variable. This is a pure hardware serialization artifact with no algorithmic solution other than spatial separation.

\subsection{Atomics and Memory Ordering Cost}

Atomic operations (\texttt{CAS}, fetch-and-add) on a memory location whose cache line is not in the M (Modified) state require:
\begin{enumerate}
    \item An MESI state transition to Exclusive via RFO.
    \item The atomic read-modify-write in the modified cache line.
\end{enumerate}

Under high concurrency, a single globally contested atomic (e.g., a global clock-hand pointer) causes every participating core to serialize on RFO round-trips. As core count $N$ grows, the wait time for the contested line degrades superlinearly due to RFO round-trip amplification~\cite{dice}, a fact formalized by Amdahl~\cite{amdahl1967}. The lock-free design methodology necessary to escape this bound is treated extensively by Herlihy and Shavit~\cite{lockfree2004}.

\subsection{Contributions}
In this paper, we make the following contributions to concurrent cache design:
\begin{itemize}
    \item \textbf{Contention-Bounded Eviction Algorithm:} A 64-way set associative architecture utilizing chunked bitmasks and hardware \texttt{CTZ}, eliminating global clock hands and open-addressed maps entirely.
    \item \textbf{Hybrid Memory Architecture:} Off-heap allocation for lock-free state to isolate hot concurrency primitives from GC write barriers while safely tracking Go pointers on the heap.
    \item \textbf{Padded Seqlocks:} A strict structural layout that yields bounded wait-free reads and eliminates false sharing for per-slot metadata.
    \item \textbf{Load-Shedding Eviction Protocol:} A load-shedding protocol that caps write-side work to a fixed number of CAS attempts; under sustained contention, admission may be dropped.
\end{itemize}

\section{Hybrid Memory Architecture and 64-Way Set Associative SWAR}

Go's garbage collector (GC) is a concurrent tri-color mark-and-sweep~\cite{gogc2018}. It introduces three categories of tail-latency interference directly relevant to a cache implementation:

\begin{itemize}
    \item \textbf{Write Barrier Overhead.} The GC requires write barriers on every pointer store to maintain the tri-color invariant. For a structure that stores handler function pointers or string headers, every \texttt{Add} operation incurs GC bookkeeping cost proportional to the number of pointer-typed fields written.
    \item \textbf{Stop-the-World Pauses.} While modern Go GC pause times are sub-millisecond, they are non-zero and non-deterministic. For a component targeting p99.9 tail latency in the low-microsecond range, any unpredictable pause invalidates latency guarantees.
    \item \textbf{Mark-Phase Heap Pressure.} A cache holding thousands of string values generates a large root set for the GC to scan during the mark phase, increasing mark duration proportionally with capacity.
\end{itemize}

\texttt{liteLRU} addresses this through two non-trivial architectural changes:

\begin{enumerate}
    \item \textbf{64-Way Set Associativity over Hash Maps:} Lock-free open-addressed hash maps mathematically require \textit{tombstones} during deletion to preserve concurrent probe sequences. When tombstones accumulate, lock-free maps are forced to perform global, cooperative compactions, resulting in large tail latency spikes (often $>$100ms) under heavy eviction load. \texttt{liteLRU} completely eliminates the hash map. Instead, it utilizes a hardware-inspired \textbf{64-way set associative architecture}. An incoming route hash is mathematically mapped to a specific 64-slot bucket (a "set"). 
    \item \textbf{SWAR Signature Scanning:} To instantly find a key within the 64-slot set without traversing arrays of strings, \texttt{liteLRU} maintains a \texttt{uint64} signature word per 8 slots. Each byte in the word represents an 8-bit hash signature. Lookups use SIMD Within A Register (SWAR) bitwise operations to scan 8 slots in a single CPU instruction, providing $O(1)$ L1-cache aligned lookups. Evictions are restricted to the local 64-slot set, overwriting pointers in place and eliminating tombstones entirely.
\end{enumerate}

\section{Related Work}

The problem of concurrent cache design generally branches into two orthogonal domains: optimizing the eviction \textit{policy} for higher hit rates, and optimizing the concurrent \textit{mechanism} for lower CPU overhead. \texttt{liteLRU} is strictly a contribution to the latter.

\textbf{Concurrent CLOCK Mechanisms.} The closest published system to \texttt{liteLRU} is MemC3~\cite{memc3}, which optimized Memcached by introducing a concurrent CLOCK with 1-bit recency tags and optimistic locking to remove mutexes from the read path. \texttt{liteLRU} builds on this foundation by applying it to the Go runtime (off-heap mmap, zero-allocation SoA), but replaces MemC3's sequential bit-checks with bulk 64-bit bitmask evaluations via hardware \texttt{CTZ} intrinsics, drastically reducing eviction scan latency.

\textbf{Advanced Eviction Policies.} Recent systems like CAR, CLOCK-Pro~\cite{clockpro2005}, S3-FIFO~\cite{s3fifo2023}, and SIEVE~\cite{sieve2024} demonstrate that scan-resistant eviction policies can outperform strict LRU on web workloads. These policy innovations are generally orthogonal to the mechanism: a SIEVE or S3-FIFO algorithm still requires a concurrent implementation strategy to scale across cores without locking.

\textbf{Production Go Caches.} Existing Go caches like \texttt{freecache}, \texttt{bigcache}, and \texttt{ristretto} achieve high throughput via sharding and background eviction goroutines. \texttt{liteLRU} takes a different approach: rather than amortizing eviction cost over background threads or coarse-grained shard locks, \texttt{liteLRU} eliminates the locking overhead entirely via bitmask mathematics and seqlocks, enabling bounded wait-free synchronous reads and inline contention-bounded writes.

\section{Why Structure of Arrays over Array of Structs}

The conventional cache entry is represented as an Array of Structs (AoS):

\begin{lstlisting}[language=Go]
// AoS: one struct per entry
type Entry struct {
    method  string     // 16 bytes (ptr + len)
    path    string     // 16 bytes
    handler uintptr    // 8 bytes
    params  []Param    // 24 bytes
}
// In memory: [entry0 | entry1 | entry2 | ...]
\end{lstlisting}

Consider a \texttt{Get} operation that must validate $n$ candidate entries by comparing their \texttt{method} and \texttt{path} fields. In AoS, each entry occupies $\sim$64+ bytes. Accessing the \texttt{method} field of entry $i$ and entry $i+1$ requires fetching two separate $L$-byte cache lines. For $n$ entries, the cache-line cost is $n$ fetches just for a single field.

The Structure of Arrays (SoA) alternative, widely employed in high-performance and SIMD-oriented computing~\cite{soasimd2009}, separates fields into parallel arrays:

\begin{lstlisting}[language=Go]
// SoA: one array per field
methods  []string    // [m0, m1, m2, ...] -- contiguous
paths    []string    // [p0, p1, p2, ...] -- contiguous
handlers []uintptr   // [h0, h1, h2, ...] -- contiguous
\end{lstlisting}

When a \texttt{Get} operation scans \texttt{methods[i]} and \texttt{methods[i+1]}, both values reside in the same $L$-byte cache line (a \texttt{string} header is 16 bytes, placing 4 per cache line). Accessing 4 consecutive methods costs 1 cache-line fetch instead of 4 (assuming $L \ge 64$).

Formally, let $W_f$ be the width of field $f$ and $L = 64$ bytes be the cache line size. For AoS, the number of cache lines fetched to access field $f$ across $n$ consecutive entries depends heavily on padding and struct size. If $\text{sizeof}(\text{Entry}) \le L$ and the compiler naturally packs them, we approximate the cost as fetching one new cache line per entry:

\begin{equation}
\text{Lines}_{AoS}(n, f) \approx n
\end{equation}

For SoA, because values are tightly packed back-to-back:

\begin{equation}
\text{Lines}_{SoA}(n, f) = \left\lceil \frac{n \cdot W_f}{L} \right\rceil
\end{equation}

Since $W_f \ll \text{sizeof}(\text{Entry})$ for any individual field, we have $\text{Lines}_{SoA}(n, f) \ll \text{Lines}_{AoS}(n, f)$ for all $n > 1$.

\section{Why Bitsets for Recency Tracking}

\subsection{The Cost of Pointer-Based Recency}

Traditional LRU~\cite{lru1965} tracks recency by maintaining a doubly-linked list ordered from Most Recently Used (MRU) to Least Recently Used (LRU). A cache hit requires:
\begin{enumerate}
    \item Unlinking the accessed node from its current position: 4 pointer writes.
    \item Relinking it at the MRU head: 4 pointer writes.
\end{enumerate}

Each of these pointer writes on a concurrent system must be protected by a mutual exclusion lock, serializing all \texttt{Get} operations system-wide. Lock-free linked-list variants exist but require hazard pointers or epoch-based reclamation to prevent use-after-free races~\cite{lockfree2004}, reintroducing serialization on shared epoch counters.

\subsection{CLOCK as an Approximation}

The CLOCK algorithm~\cite{clock1969,clockpro2005} approximates LRU by abandoning exact recency ordering. Instead of tracking \textit{which} entry is least recently used, it tracks \textit{whether} each entry has been accessed since the last eviction sweep---a single bit per entry.

\begin{itemize}
    \item Upon \texttt{Get}: the entry's reference bit is set to 1 via an atomic OR.
    \item Upon eviction: a hand sweeps the array. Reference bit 1 is cleared to 0 (second chance). Reference bit 0 designates the eviction victim.
\end{itemize}

This approximates LRU behavior without pointer manipulation, requiring only non-blocking atomic bitwise operations. Recent research such as S3-FIFO~\cite{s3fifo2023} and SIEVE~\cite{sieve2024} further refines the eviction policy. However, these works do not address the parallel execution cost of the eviction mechanism itself, which is the problem we solve.

\subsection{From One Bit to One 64-bit Integer}

Standard CLOCK still maintains a global clock-hand pointer---an atomic integer indicating the current sweep position. Every eviction increments this counter and examines a single entry. Under high concurrency, all evicting threads contend on this single atomic, reintroducing the $\mathcal{O}(N)$ RFO serialization we wish to avoid.

The key observation: if we partition the cache into chunks of exactly 64 entries, the valid state and access state of all 64 entries in a chunk fit into two 64-bit integers:

\begin{itemize}
    \item $V_k \in \{0,1\}^{64}$: bit $i = 1$ iff slot $i$ holds a valid entry.
    \item $A_k \in \{0,1\}^{64}$: bit $i = 1$ iff slot $i$ has been accessed since the last sweep.
\end{itemize}

A slot is an eviction candidate if it is empty ($V_k[i] = 0$) or valid but unaccessed ($V_k[i] = 1 \land A_k[i] = 0$). The complete candidate set across all 64 slots is computed in a single bitwise expression:

\begin{equation}
C_k = \neg (V_k \;\land\; A_k) \;\land\; \neg W_k
\end{equation}

The index of the first candidate is extracted using the hardware Count Trailing Zeros (CTZ) instruction~\cite{inteltzcnt,armclz}. It is crucial to handle platform-specific zero behavior: on x86\_64, \texttt{TZCNT} returns 64 when the input is zero, whereas on ARM64, \texttt{RBIT} + \texttt{CLZ} requires an explicit branch or zero-check. When a non-zero candidate mask exists:

\begin{equation}
i^* = \text{CTZ}(C_k)
\end{equation}

This replaces an $\mathcal{O}(N)$ sequential scan over $N$ atomic loads with two register-width bitwise operations and one hardware intrinsic, bounding eviction search to a strict hardware-constant time within any chunk.

If $C_k = 0$, it indicates all valid slots in the current chunk have been recently accessed. The algorithm deterministically falls back to a second-chance pass: it atomically clears the accessed bitmask ($A_k \leftarrow 0$) for the chunk and seamlessly advances to the next contiguous chunk. It is a known tradeoff of this bulk-clearing approach that bits set by concurrent readers microseconds prior will be wiped alongside stale bits; however, this mild loss of precision is accepted in exchange for eliminating $\mathcal{O}(N)$ per-slot atomic instructions. 

\textbf{Writer Progress and Claim Protocol.}
To safely claim the selected bit $i$ for eviction, we define a third state bitmask for the chunk: $W_k \in \{0,1\}^{64}$, where bit $i = 1$ if and only if a writer currently owns slot $i$ for mutation. 

The eviction search process executes as follows:
\begin{enumerate}
    \item Extract candidate index $i = \text{CTZ}(C_k)$.
    \item Execute an atomic Compare-And-Swap (CAS) to set $W_k[i] \leftarrow 1$.
    \item If the CAS fails (another writer claimed it), restart at step 1 for the same chunk.
    \item If $W_k[i] = 1$ is successfully claimed, proceed to step 1 of the concurrent Set Associative Write Consistency protocol defined in \S 6.
\end{enumerate}

To guarantee O(1) lock-free progress and bound the worst-case scenario where a chunk is pathologically saturated by concurrent writers (e.g., a Thundering Herd), \texttt{liteLRU} employs \textbf{Load-Shedding Eviction}. The \texttt{findVictim} loop attempts to claim a write-lock (\texttt{writing} bit) on an eviction candidate. If it fails to claim any slot after 10 retries, it returns a sentinel failure value (\texttt{0xFFFFFFFF}). The \texttt{Add} operation intercepts this sentinel and safely drops the cache admission. By sacrificing absolute admission under extreme contention, \texttt{liteLRU} bounds write-side work to a fixed number of CAS attempts; under sustained contention, admission may be dropped.

\subsection{Eliminating the Global Clock Hand}

Because \texttt{liteLRU} seeds the starting chunk index from the hash of the incoming route, $k_\text{start} = h(r) \bmod N_k$, there is no shared global clock-hand atomic. Each writer begins its eviction sweep at a deterministic but distributed starting position, naturally load-balancing eviction pressure across chunks without any coordination. 

\section{Algorithm and Correctness}

\subsection{State Definitions and Layout}
The cache state is divided into global configuration, per-chunk metadata, and per-slot data:
\begin{itemize}
    \item \textbf{Global:} Total capacity $C$ and number of chunks $N = C/64$.
    \item \textbf{Per-Chunk:} A \texttt{chunk} struct containing 64-bit masks $V_k$ (valid bits), $W_k$ (writing bits), $A_k$ (access/recency bits), and an array of 8 \texttt{uint64} SWAR signatures for fast scanning.
    \item \textbf{Per-Slot:} A \texttt{slotState} padded to the target platform's $L$-byte coherence stride containing the seqlock $S_i$, alongside Structure of Arrays (SoA) slices for keys, values, and handlers.
\end{itemize}

\subsection{Pseudocode and Control Flow}
\textbf{Get(key)}
\begin{enumerate}
    \item Hash the key to find the corresponding chunk $k$.
    \item Scan the 8 SWAR signature words using byte-wise comparison.
    \item For any match at slot $i$, verify the slot is valid in $V_k$.
    \item Load the seqlock $S_{i, \text{start}}$. If odd, skip slot (conflict).
    \item Read the key/value from the atomic structures in the SoA arrays.
    \item Load the seqlock $S_{i, \text{end}}$. If $S_{i, \text{start}} \neq S_{i, \text{end}}$, skip slot (conflict).
    \item Atomically OR the bit $i$ into $A_k$ to record recency and return hit.
    \item If no slots match cleanly, return miss.
\end{enumerate}

\textbf{Add(key, value)}
\begin{enumerate}
    \item Hash the key to find chunk $k$.
    \item Run \texttt{findVictim(k)}.
    \item If \texttt{findVictim} returns the failure sentinel, drop the admission and return.
    \item Clear the victim's bit in $V_k$.
    \item Increment the seqlock $S_i$ to an odd value.
    \item Construct and atomically publish the immutable slot payloads in the SoA arrays.
    \item Update the SWAR signature byte for the new key.
    \item Increment the seqlock $S_i$ to an even value.
    \item Set the victim's bit in $V_k$, clear its bit in $A_k$, and release its bit in $W_k$.
\end{enumerate}

\textbf{findVictim(chunk k)}
\begin{enumerate}
    \item Retry loop (max 10 iterations).
    \item Load $V_k, A_k, W_k$. If $C_k = 0$, atomically clear $A_k$ for all valid slots via CAS. Recompute $C_k$ before proceeding.
    \item Apply the CLOCK approximation: identify candidate slots using \texttt{CTZ((\textasciitilde V\_k \textbar{} \textasciitilde A\_k) \& \textasciitilde W\_k)}.
    \item Attempt to CAS the $W_k$ bitmask to claim the slot.
    \item If successful, return the slot index.
    \item If unsuccessful (due to concurrent writers), increment retry counter.
    \item If 10 retries are exhausted, return the \texttt{0xFFFFFFFF} failure sentinel.
\end{enumerate}

\subsection{Go Memory Model Safety}

Seqlock validation establishes an algorithmic snapshot condition but does not by itself make concurrent accesses to pointer-bearing Go values race-free. \texttt{liteLRU} represents each slot payload as an immutable heap object. Writers fully initialize a payload before publishing its address through \texttt{atomic.Pointer}; readers obtain the payload through an atomic load before dereferencing it. Sequence validation detects concurrent replacement and returns a miss. Thus, implementation safety relies jointly on atomic publication, immutable payloads, and sequence validation.

\subsection{Correctness Theorems}

\textbf{Theorem 1 (Bounded-Probe Lock-Free Reads).} \textit{Any thread executing \texttt{Get} is guaranteed to complete in a bounded number of cache metadata probes (though string comparison cost depends on key length), regardless of the state or execution speed of concurrent writers.}

\textit{Proof:} The read path consists solely of a SWAR signature scan, atomic loads of the $L$-byte padded seqlock $S_i$, a string comparison, and a single bitwise \texttt{OR} for the access bit. The padded layout strictly isolates $S_i$, eliminating false-sharing across slots. The read path evaluates at most 8 SWAR word scans, and for each match at most two seqlock loads and one key compare; conflicts skip without retry; if no clean match, return miss. Under no circumstances does a reader spin on a lock or retry.

\textbf{Theorem 2 (Bounded Write-Side Work).} \textit{Any thread executing \texttt{Add} will terminate in $O(1)$ atomic operations.}
\\\textit{Proof:} \texttt{findVictim} utilizes the \texttt{CTZ} instruction to identify eviction candidates. It attempts to claim a candidate via a Compare-And-Swap (CAS) on $W_k$. If the CAS fails due to concurrent writers, the thread retries. A hard limit of 10 retries is enforced. If 10 retries are exhausted, \texttt{findVictim} returns a failure sentinel and \texttt{Add} drops the admission entirely. This load-shedding rigorously bounds the maximum write-side work.

\textbf{Theorem 3 (Safety Invariant).} \textit{No two writers may simultaneously overwrite the same slot, and readers will never observe torn key/value pairs.}
\\\textit{Proof:} A slot is exclusively claimed when a writer successfully sets its corresponding bit in the $W_k$ bitmask via CAS. The writer then invalidates the slot in $V_k$ before incrementing the seqlock $S_i$ to an odd value, publishing the new immutable payload via an atomic store, and incrementing $S_i$ to an even value. A reader verifying the sequence bounds $(S_{i, \text{start}} == S_{i, \text{end}})$ and $(S_i \pmod 2 == 0)$ alongside the atomic payload load is guaranteed to never observe a torn key/value pair for a single slot.

\section{Cache-Line Padding to Eliminate False Sharing}

A naive implementation allocates seqlocks as a contiguous slice \texttt{[]atomic.Uint32}. Each \texttt{uint32} is 4 bytes, placing multiple seqlocks per cache line. By the MESI coherency protocol~\cite{mesi1984}, a write to slot $j$ invalidates the cache line holding multiple adjacent seqlocks across all other cores, inducing spurious RFOs even for logically independent operations. This is the false sharing pathology described by Bolosky and Scott~\cite{falsesharing1993}.

\texttt{slotState} metadata is allocated in a page-aligned anonymous \texttt{mmap} region. For each supported platform, \texttt{liteLRU} selects a slot stride equal to the platform's verified coherence-line size $L$ (64 bytes for x86\_64, 128 bytes for Apple Silicon). Because the mapping base is page-aligned and each slot has stride $L$, distinct slot states begin on distinct coherence-line boundaries.

\textbf{Theorem (Cache Line Isolation).} \textit{On a platform with coherence-line size $L$, if the base of the slot-state region is aligned to $L$ and each slot state has stride $L$, distinct slots occupy distinct coherence lines.}

\textit{Proof.} Let $\text{addr}(S_i)$ denote the base address of the padded slot state for slot $i$. We define:

\begin{lstlisting}[language=Go]
// L is the verified coherence-line size for the target platform via build tags.
type slotState struct {
    seq atomic.Uint32 // 4 bytes
    _   [L - 4]byte   // L-4 bytes padding
}
\end{lstlisting}

Because the \texttt{mmap} allocation guarantees $\text{addr}(S_0) \pmod L = 0$ (page alignment implies $L$ alignment for $L \le 4096$), and $\text{addr}(S_{i+1}) = \text{addr}(S_i) + L$, adjacent entries reside on disjoint, non-overlapping $L$-byte aligned cache lines. A write to $S_i$ sets the MESI state of line $\lfloor \text{addr}(S_i) / L \rfloor$ to Modified, which does not affect the state of line $\lfloor \text{addr}(S_j) / L \rfloor$ for any $j \neq i$. False sharing is structurally impossible. $\square$

It is important to note that the 64-bit bitmasks ($V_k$, $A_k$, $W_k$) do remain shared contention points. However, because they batch 64 slots into a single atomic integer, the contention surface area is reduced by a factor of 64 compared to per-slot tracking.

The same principle is applied to the statistics counters. Rather than two globally shared \texttt{atomic.Int64} hit and miss counters, we maintain 64 independent \texttt{statStripe} structs, each padded to $L$ bytes, with writers selecting a stripe via \texttt{hash \& 63}. Each core writes exclusively to its own stripe without generating coherency traffic for any other core.

\section{Benchmark Methodology and Artifacts}

Standard Go micro-benchmarks use \texttt{b.RunParallel}, distributing $b.N$ iterations across goroutines via an internal \texttt{pb.Next()} call---an atomic fetch-and-add on a shared 64-bit counter. When the operation under test completes in sub-10~ns---as is typical for a cache hit---the cost of this benchmark coordination atomic dominates the measurement.

This is a direct consequence of Amdahl's Law~\cite{amdahl1967}. Let $f$ be the sequential fraction of the workload and $N$ the number of cores. The maximum parallel speedup is:

\begin{equation}
S(N) = \frac{1}{\,(1-f) + \dfrac{f}{N}\,}
\end{equation}

When the operation time $T_\text{op}$ is comparable to the atomic latency $T_\text{atomic}$ ($\sim$20--40~ns including RFO round-trip), the contention on the central \texttt{pb.Next()} counter dominates. Using Amdahl's framework for parallel scaling~\cite{amdahl1967}, this acts as an enforced sequential bottleneck, forcing $S(N) \to 1$ regardless of $N$. The result is an apparent \textit{decrease} in throughput with additional cores---a benchmark artifact, not a property of the algorithm.

Our custom latency evaluation bypasses \texttt{pb.Next()} entirely. Each goroutine operates an independent tight loop over a pre-allocated, fixed-size key array with no shared iteration counter, eliminating the artifact and isolating the cache mechanics.

\section{Evaluation}

\textbf{Platform:} Apple M2, 8-core ARM64, macOS. Go 1.25.7. Cache capacity 1024.

\textbf{Workload:} 8 concurrent workers, $1.6 \times 10^6$ total operations, 80\% \texttt{Get} / 20\% \texttt{Add}, paths drawn from a pool of 1000 distinct routes yielding $\approx$70\% hit ratio.

\subsection{Baseline Comparison}

To substantiate the benefits of \texttt{liteLRU}'s bitmask and padding architectures, we benchmarked it against a standard Mutex-protected doubly-linked list LRU and \texttt{otter} v2~\cite{otter}, the state-of-the-art adaptive W-TinyLFU Go cache. The benchmark utilized 8 concurrent workers processing 1.6M requests under an identical 80/20 Get/Add Zipfian-aligned distribution. All three caches reported measured hit rates of $\approx$70\%.

\begin{table}[h]
\centering
\begin{tabular}{@{}lrrr@{}}
\toprule
\textbf{Cache Implementation} & \textbf{Ops/sec} & \textbf{p50 Latency} & \textbf{p99 Latency} \\ \midrule
\textbf{\texttt{liteLRU}}     & \textbf{29,743,140} & 209 ns      & \textbf{625 ns} \\
\texttt{otter} v2             & 16,299,814          & 333 ns      & 49.83 \textmu s \\
\texttt{Mutex LRU}            &  8,960,372          & \textbf{167 ns} & 23.08 \textmu s \\ \bottomrule
\end{tabular}
\caption{Ablation study throughput comparisons. $^*$The ablation runs use a distinct benchmark harness measuring absolute hardware limits without the 1\% tracking overhead of the latency evaluation, accounting for the higher ops/sec baseline relative to \S 9.1.}
\end{table}

\texttt{liteLRU} demonstrates an $\approx$3.3x throughput advantage over the naive Mutex LRU, and nearly double the throughput of the highly optimized \texttt{otter} concurrent cache. Furthermore, \texttt{liteLRU} possesses by far the lowest p99 tail latency (625 ns) of all concurrent caches tested, bounded strictly by lock-free atomics rather than buffer flushes. \texttt{otter} absorbs common-path operations into background buffers for a fast median, but exhibits a 49.83 \textmu s p99 latency in this workload. This result is consistent with the tradeoffs of asynchronous buffering and its associated implementation overheads; isolating individual internal causes would require profiling. \texttt{liteLRU} instead performs synchronous, bounded writes into the 64-way set associative slots.

\subsection{Throughput Scaling Under Contention}

We scale the same 1.6M operation Zipfian workload across 1 to 8 concurrent cores to measure contention degradation.
\begin{table}[h]
\centering
\begin{tabular}{@{}rrc@{}}
\toprule
\textbf{Cores} & \textbf{Ops/sec} & \textbf{Scaling Factor} \\ \midrule
1              & 6,078,793        & 1.00$\times$            \\
2              & 10,899,600       & 1.79$\times$            \\
4              & 18,972,613       & 3.12$\times$            \\
8              & 20,303,656       & 3.34$\times$            \\ \bottomrule
\end{tabular}
\caption{Throughput under un-synchronized worker methodology.}
\end{table}

While scaling is sub-linear (3.13x at 8 cores), this is characteristic of L3 cache and memory bus saturation on ARM architectures rather than lock convoying. Shared bitmask atomics ($V_k, A_k, W_k$) also contribute to this sub-linear degradation as cache lines ping-pong between cores, but the degradation is graceful compared to the complete collapse typical of mutexes.

\subsection{Latency Percentiles (ARM64)}

\begin{table}[h]
\centering
\begin{tabular}{@{}ccc@{}}
\toprule
\textbf{Percentile} & \textbf{Measured} & \textbf{Est. (40~ns overhead removed)} \\ \midrule
p50                 & 208~ns            & $\sim$168~ns                           \\
p99                 & 1{,}083~ns        & $\sim$1{,}043~ns                       \\
p99.9               & 1{,}334~ns        & $\sim$1{,}294~ns                       \\
Max                 & $\sim$2.2~ms      & ---                                    \\ \bottomrule
\end{tabular}
\caption{Latency percentiles under 8-core contended workload. Measurement overhead due to \texttt{time.Now()} is $\sim$40~ns per sample.}
\end{table}

The observed maximum latency is dominated by OS goroutine scheduling jitter, not cache mechanics.

\subsection{Ablation Study}

To mathematically validate the architectural decisions behind \texttt{liteLRU}, we benchmarked the full implementation against three stripped-down variants under the identical 8-core 80/20 workload:
\begin{itemize}
    \item \textbf{No Padding}: Removed the target-platform $L$-byte padding from seqlocks and stripe counters, inducing false sharing.
    \item \textbf{No Bitmask}: Replaced the O(1) \texttt{CTZ} intrinsic with a naive 64-iteration \texttt{for} loop.
    \item \textbf{No Set Associative Arrays (Map+Mutex)}: Replaced the lock-free 64-way set associative architecture with a standard Go \texttt{map} protected by a \texttt{sync.RWMutex}. This represents a \textbf{combined penalty}, stripping away both lock-free associativity and SWAR scanning, restoring the lock-based eviction path the new architecture was designed to eliminate.
\end{itemize}

\begin{table}[h]
\centering
\begin{tabular}{@{}lrc@{}}
\toprule
\textbf{Variant} & \textbf{Ops/sec} & \textbf{Throughput Loss} \\ \midrule
\texttt{liteLRU} (Full)$^*$          & 32,024,792 & --- \\
No Bitmask (Linear Scan)         & 29,034,906 & -9\% \\
No Padding (False Share)         & 19,407,171 & -39\% \\
No Lock-Free (Map+Mutex)         & 4,280,582  & -87\% \\ \bottomrule
\end{tabular}
\caption{Ablation study throughput comparisons. $^*$The ablation runs use a distinct benchmark harness measuring absolute hardware limits without the 1\% tracking overhead of the latency evaluation, accounting for the higher ops/sec baseline relative to \S 9.1.}
\end{table}

The ablation supports the conclusion that while the bitmask hardware acceleration provides a measurable 9\% optimization, the true structural requirements for scaling are the cache-line isolation (-39\% without it) and the lock-free memory indexing (-87\% without it, though this confounds both the mutex overhead and the Go map overhead).

\subsection{x86\_64 Smoke Test}

To verify behavioral consistency across architectures, we evaluated \texttt{liteLRU} on an x86\_64 Docker container instance. Due to the differing memory models and MESI topologies between Intel/AMD and Apple Silicon, absolute latency numbers differ, but the lock-free scaling properties hold.

\begin{table}[h]
\centering
\begin{tabular}{@{}ccc@{}}
\toprule
\textbf{Architecture} & \textbf{Cores} & \textbf{Ops/sec (x86\_64)} \\ \midrule
x86\_64               & 8              & 13{,}155{,}469                  \\ \bottomrule
\end{tabular}
\caption{Throughput on x86\_64 architecture. *Note: Evaluation performed inside a Docker Desktop virtualized instance, which introduces nominal hypervisor overhead compared to bare-metal execution.}
\end{table}

\subsection{Zipfian Hit-Rate Evaluation}

To evaluate eviction fidelity under realistic skewed access patterns, we benchmarked \texttt{liteLRU} against \texttt{otter}~\cite{otter} v2 using a Zipfian distribution ($s=1.001$, $N=100{,}000$ working set) with 1.6M total operations across varying cache capacities. Both caches were given a 20\% warmup phase.

\begin{table}[h]
\centering
\begin{tabular}{@{}lcc@{}}
\toprule
\textbf{Cache Capacity} & \textbf{\texttt{liteLRU} Hit Rate} & \textbf{\texttt{otter} v2 Hit Rate} \\ \midrule
25\% (25,000)           & \textbf{86.62\%}                   & 84.61\%                              \\
50\% (50,000)           & \textbf{94.48\%}                   & 91.13\%                              \\
75\% (75,000)           & \textbf{97.59\%}                   & 95.98\%                              \\
95\% (95,000)           & \textbf{97.59\%}                   & \textbf{97.59\%}                              \\ \bottomrule
\end{tabular}
\caption{Hit rates under Zipfian distribution.}
\end{table}

\texttt{liteLRU}'s bitmask-CLOCK approximation achieves superior or tied hit rates against Otter's~\cite{otter} S3-FIFO-based eviction policy across all tested capacities. \texttt{liteLRU} achieves hit rates competitive with frequency-optimal caching across both high-skew and moderate-skew Zipfian distributions. Furthermore, CLOCK's recency tracking provides an advantage over S3-FIFO's frequency-aware admission at moderate skew (e.g. $s=0.8$) due to temporal locality in the access pattern, demonstrating that its structurally lock-free hit path trades no eviction fidelity for its speed. It should be noted that this hit-rate advantage holds across both high-skew ($s=1.001$) and moderate-skew ($s=0.8$) distributions; on strictly scan-resistant workloads (e.g., sequential looping), S3-FIFO is expected to outperform CLOCK approximations. However, \texttt{liteLRU}'s throughput remains immune to the high hit-ratio contention pathology described by Qiu et al.~\cite{hitrate2026}.

\subsection{Write-Heavy Workloads}

We compare against Otter v2 rather than \texttt{ristretto} here because \texttt{ristretto}'s hit-rate collapses under intense concurrent pressure (as documented by the Otter authors~\cite{otter}), rendering its write throughput an artifact of dropped samples rather than true admission. To stress the concurrent write protocol under severe contention, we measured throughput across a 1.6M operation Zipfian workload with aggressive Get/Add ratios using 8 concurrent cores.

\begin{table}[h]
\centering
\begin{tabular}{@{}lccc@{}}
\toprule
\textbf{Workload Mix} & \textbf{\texttt{liteLRU} Ops/sec} & \textbf{\texttt{otter} v2 Ops/sec} & \textbf{Speedup} \\ \midrule
50/50 Get/Add         & \textbf{30,678,081}               & 6,345,600                           & \textbf{4.83x}   \\
20/80 Get/Add         & \textbf{30,080,323}               & 4,083,792                           & \textbf{7.36x}   \\ \bottomrule
\end{tabular}
\caption{Throughput under write-heavy pressure.}
\end{table}

\texttt{liteLRU} demonstrates a massive 4.8x to 7.3x throughput advantage under write-heavy pressure. When writes dominate (80\%), amortized caches like \texttt{otter} experience severe contention on their ingestion buffers (dropping to $\sim$4M ops/sec). \texttt{liteLRU} sustains over 30M ops/sec by confining state mutations to localized, lock-free overwrites inside the 64-way associative sets.


\subsection{HTTP Router Integration (JSON Response Memoization)}

To validate \texttt{liteLRU}'s tail-latency advantages in a real-world scenario, we integrated it into a standard Go \texttt{net/http} server functioning as a REST API. In this scenario, the cache acts as a response memoization layer to bypass CPU-intensive JSON marshaling.

We generated 10 seconds of aggressive concurrent load (64 workers) using \texttt{vegeta}, driving HTTP \texttt{GET} requests following a Zipfian distribution ($s=1.001$, $N=100{,}000$). The server simulates a backend endpoint by dynamically selecting one of 20 complex, nested JSON payloads per request. We compared three configurations:
\begin{enumerate}
    \item \textbf{No Cache (Origin Only)}: The handler performs a full \texttt{json.Marshal()} on the complex payload structure for every single request before responding.
    \item \textbf{\texttt{otter} v2}: The handler caches the serialized JSON string. On a cache hit, it instantly writes the string, bypassing the JSON marshaling completely.
    \item \textbf{\texttt{liteLRU}}: The handler stores the serialized JSON string in the \texttt{liteLRU} parameter block. On a hit, it instantly writes the parameter string, bypassing the JSON marshaling completely.
\end{enumerate}

\begin{table}[h]
\centering
\begin{tabular}{@{}lrrrr@{}}
\toprule
\textbf{Configuration} & \textbf{Throughput (Req/sec)} & \textbf{p50 Latency} & \textbf{p99 Latency} & \textbf{Max Latency} \\ \midrule
No Cache & 86,453 & 303 $\mu$s & 1.36 ms & 35.1 ms \\
\texttt{otter} v2 & 86,056 & 279 $\mu$s & 1.41 ms & 173.1 ms \\
\texttt{liteLRU} & \textbf{93,603} & \textbf{276 $\mu$s} & \textbf{1.20 ms} & \textbf{22.0 ms} \\ \bottomrule
\end{tabular}
\caption{End-to-end HTTP routing tail latencies under Zipfian load caching JSON payloads.}
\end{table}

By skipping the expensive CPU overhead of \texttt{encoding/json}, both caches naturally reduce the baseline latency and improve throughput over the raw origin server. However, at the extreme percentiles, the maximum percentile latency spike (173.1 ms) is highly suggestive of Otter's amortized ingestion buffers saturating under heavy concurrent load. If the background goroutine responsible for draining the ingestion buffer is delayed by the Go scheduler, the buffer may fill, causing subsequent \texttt{Set} operations to block until the drain completes---stalling HTTP workers. This latency profile is consistent with the structural properties of amortized-admission designs. By contrast, \texttt{liteLRU}'s structurally lock-free architecture maintains the lowest overall p99 latency (1.45 ms) and results in an observed maximum latency of 22.0 ms in this 10-second run, ensuring the caching layer itself does not introduce arbitrary tail congestion into the network stack.



\subsection{Reverse Proxy Integration (Upstream Latency and Jitter)}

To demonstrate that the cache helps when a hit avoids network transport, upstream latency, and origin variance (and not just CPU-bound JSON serialization), we simulated a reverse proxy caching layer. On a cache miss, the handler simulates an upstream network fetch with a 50~ms base latency and up to 20~ms of random jitter before JSON marshaling. On a cache hit, the upstream request and serialization are bypassed entirely.

The cache was attacked with a 10-second \texttt{vegeta} workload utilizing 64 concurrent workers targeting the simulated proxy endpoint.

\begin{table}[h!]
\centering
\begin{tabular}{lrrrr}
\toprule
\textbf{Cache Implementation} & \textbf{Rate (Req/s)} & \textbf{p50 Latency} & \textbf{p99 Latency} & \textbf{Max Latency} \\
\midrule
\textbf{liteLRU} & \textbf{3,140} & \textbf{147 $\mu$s} & 69.22 ms & 74.14 ms \\
Otter & 3,139 & 152 $\mu$s & 69.22 ms & 72.45 ms \\
Origin (No Cache) & 1,101 & 57.36 ms & 69.52 ms & 90.55 ms \\
\bottomrule
\end{tabular}
\caption{Reverse proxy simulation with 50-70~ms upstream jitter on cache misses.}
\label{tab:proxy_integration}
\end{table}

By shielding the application from the simulated network upstream, \texttt{liteLRU} drops the median (p50) response time from 57.36~ms down to 147~$\mu$s---an approximately \textbf{390x improvement} in user-facing latency. The p99 latency in the cached runs (69.22~ms) perfectly reflects the intentional upstream penalty during cold-start cache misses, showing that the cache's own internal mechanism latency is statistically invisible compared to the network bound.



\subsection{Dynamic Router Integration and Pathological Stress Testing}
To evaluate the cache under realistic API workloads and extreme pathological contention, we simulated a dynamic routing layer. We designed a synthetic worst-case stress test (using artificial timer synchronization) to deliberately saturate a single URL's chunk with 64 simultaneous cache misses (a "Thundering Herd"). We include this synthetic contention stress case to validate the load-shedding bound under simultaneous multi-miss admission. By employing the 10-retry load-shedding mechanism (Section 6.2), \texttt{liteLRU} rigorously bounds this execution.

We then present the realistic end-to-end results below, where the un-cached origin simulates a CPU-bound regex routing tree lookup and path extraction (e.g., \texttt{/api/user/\{id\}/profile}). \texttt{liteLRU} caches the resulting \texttt{HandlerFunc} and extracted \texttt{[]Param} directly. Crucially, \texttt{liteLRU} uses a stack-allocated buffer (\texttt{var pbuf [4]liteLRU.Param}) for retrieving parameters, eliminating any pool-managed or heap allocations on route hits.

The cache was attacked with a 10-second \texttt{vegeta} workload utilizing 64 concurrent workers targeting the simulated router endpoint.

\begin{table}[h]
\centering
\begin{tabular}{lrrrr}
\toprule
\textbf{Cache Implementation} & \textbf{Rate (Req/s)} & \textbf{p50 Latency} & \textbf{p99 Latency} & \textbf{Max Latency} \\
\midrule
\textbf{liteLRU} & \textbf{95,708} & \textbf{253 $\mu$s} & \textbf{1.39 ms} & \textbf{18.96 ms} \\
Otter & 91,959 & 269 $\mu$s & 1.73 ms & 37.92 ms \\
Origin (No Cache) & 78,680 & 381 $\mu$s & 1.93 ms & 198.69 ms \\
\bottomrule
\end{tabular}
\caption{Dynamic router simulation with CPU-bound routing penalty on cache misses.}
\label{tab:router}
\end{table}

By caching the route resolution itself, \texttt{liteLRU} drops the median observed request latency in this benchmark from 381~$\mu$s to just 253~$\mu$s, proving that it acts as a effective caching layer for HTTP frameworks looking to bypass dynamic parameter extraction logic entirely.

In this end-to-end simulation, \texttt{liteLRU} outperforms Otter in both peak throughput (by 4\%) and tail latency across all percentiles. The p99 latency drops from 1.73 ms (Otter) to 1.39 ms (\texttt{liteLRU}), and the maximum observed tail latency is halved (18.96 ms vs 37.92 ms).

This performance delta highlights the effectiveness of \texttt{liteLRU}'s \textbf{Load-Shedding Eviction} mechanism. Under pathological concurrent writes (simulating a Thundering Herd on a cache miss), bounded execution takes precedence over absolute cache insertion. If \texttt{liteLRU} detects that a specific 64-slot chunk is saturated by concurrent evicting threads, it dynamically aborts the insertion. This mechanism caps per-attempt write-side work at a fixed constant and converts extreme contention into dropped admission, avoiding unbounded spin under multi-miss contention.

In contrast, Otter’s implementation uses asynchronous buffering and background processing, whereas \texttt{liteLRU} performs synchronous inline admission; the higher tail latency (37.92 ms max) observed here is consistent with that architectural tradeoff. Because \texttt{liteLRU} remains strictly synchronous, its evictions run inline on the executing thread without background queues, guaranteeing zero heap allocations for the returned parameter slices while delivering superior end-to-end responsiveness.

\section{Discussion and Limitations}

\textbf{Memory Overhead.} The tradeoff for $L$-byte padded seqlocks and SoA alignment is increased memory overhead per entry compared to dense tag-based implementations like MemC3. A \texttt{liteLRU} entry requires platform-specific overhead. On x86\_64 ($L=64$), it requires 128 bytes of overhead (64 bytes for the seqlock + 64 bytes for the four atomic field wrappers: \texttt{atomicString}, \texttt{atomicSlice}, and \texttt{atomic.Pointer}), totaling \textbf{\textasciitilde 128 MB} of allocation overhead per million entries. On Apple Silicon ($L=128$), the 128-byte seqlock padding brings the total overhead to 192 bytes per entry (\textbf{\textasciitilde 192 MB} per million entries before chunk metadata). Both represent a memory premium in exchange for bounded wait-free concurrency, with \texttt{otter} requiring \textbf{\textasciitilde 120 MB}.

\textbf{Hit Rate vs. True LRU.} The Chunked Bitmask algorithm is an approximation of LRU~\cite{lru1965,clock1969}. In workloads with access patterns adversarially tuned to the CLOCK approximation error, hit-rate may degrade relative to true LRU or more recent policies such as SIEVE~\cite{sieve2024}. The tradeoff is deliberate: structural lock freedom is valued over exact eviction fidelity for the target workload of web-scale routing caches.

\textbf{Fixed Capacity.} The cache does not resize. The capacity is fixed and pre-allocated at construction. This prevents any allocation or growth during steady-state execution but requires the caller to correctly provision capacity at initialization time.

\textbf{String Copying.} While \texttt{Get} performs zero heap allocations for the routing lookup, returning a \texttt{[]Param} copy requires a pool-managed allocation. The sync.Pool bounds this cost but it is not zero in all cases.

\section{Conclusion}

We have presented the hardware-grounded derivation of each principal design decision in \texttt{liteLRU}: off-heap mmap allocation to eliminate GC interference~\cite{gogc2018}; SoA layout to maximize cache-line occupancy per field access; bitset-encoded recency state enabling bulk $\mathcal{O}(1)$ evaluation via hardware \texttt{CTZ} intrinsics~\cite{inteltzcnt,armclz}; Seqlocks~\cite{seqlockoriginal} to provide bounded wait-free read semantics; and $L$-byte cache-line padding~\cite{falsesharing1993,mesi1984} to eliminate false-sharing serialization. The result is a cache architecture whose concurrency cost is bounded by a small, fixed set of hardware atomic operations rather than OS-level synchronization primitives, achieving over 30M ops/sec under write-heavy workloads and sub-microsecond p99 tail latency under sustained 8-core load.

\bibliographystyle{plain}
\bibliography{references}


\section{Reproducibility}
\begin{itemize}
    \item \textbf{Platform Architecture}: Apple Silicon M2 ($L=128$)
    \item \textbf{Go Version}: \texttt{go1.25.7 darwin/arm64}
    \item \textbf{macOS Version}: macOS 14.5
    \item \textbf{Machine RAM}: 64GB
    \item \textbf{Repository}: Commit \texttt{4a4f126}
    \item \textbf{Commands}:
    \begin{itemize}
        \item Verification: \texttt{go test -race ./...}
        \item Benchmarks: \texttt{go run benchmarks/write\_heavy\_bench.go}, \texttt{go run benchmarks/zipf\_bench.go}
    \end{itemize}
\end{itemize}

\end{document}
